
% Pasur is a traditional card game and requires a standard 52-card deck (no jokers) and is played by 2 to 4 players. In this paper, we focus on the two-player version, with players referred to as \textbf{Alex} and \textbf{Bob} along with the \textbf{Dealer}.

% The game begins with four cards placed face-up on the table to form the initial pool. The initial pool must not contain any Jacks. If a Jack appears among the initial four cards, it is returned to the deck and replaced. If multiple Jacks appear or a replacement is also a Jack, the dealer reshuffles and redeals.

% Once the pool cards are valid and face-up, the dealer deals four cards to each player, starting from the player on their left (assumed to be Alex). The players then take turns, starting with Alex. On each turn, a player must play one card from their hand. The played card will either:

% \begin{itemize}
%     \item Be added to the pool of face-up cards, or
%     \item Capture one or more cards from the pool.
% \end{itemize}

% If capturing is possible, the player \emph{must} capture; they may not simply add a card to the pool. Captured cards are used to calculate the players' scores at the end of the game. Table~\ref{tab:score} shows the scoring system used in Pasur. Notably, a \textbf{Sur}—which is defined below—awards 5 bonus points.

% A \textbf{Sur} occurs when a player captures all the cards from the pool in a single move. However, there are two exceptions:
% \begin{itemize}
%     \item A Sur is not possible using a Jack.
%     \item Surs cannot be scored during the final round of play.
% \end{itemize}

% \begin{table}[h!]
% \centering
% \begin{tabular}{|c|c|}
% \hline
% \textbf{Rule} & \textbf{Points} \\
% \hline
% Most Clubs & 7 \\
% Each Jack & 1 \\
% Each Ace & 1 \\
% Each \;Sur & 5 \\
% 10{\color{red}\ding{117}}& 3 \\
% 2{\ding{168}}& 2 \\
% \hline
% \end{tabular}
% \caption{Pasur Scoring System}
% \label{tab:score}
% \end{table}
% \subsubsection{A Gamplay Example}


% \input{figs/game}

Pasur is a traditional card game played with a standard 52-card deck (excluding jokers), and it supports 2 to 4 players. In this paper, we focus on the two-player variant, where the players are referred to as \textbf{Alex} and \textbf{Bob}, along with a \textbf{Dealer} who manages the game.

The game begins with four cards placed face-up on the table to form the initial pool. This pool must not contain any Jacks. If a Jack appears among the initial four cards, it is returned to the deck and replaced. If multiple Jacks are dealt, or if a replacement card is also a Jack, the dealer reshuffles and redeals.

Once the pool is valid and face-up, the dealer deals four cards to each player, starting with the player on their left (assumed to be Alex). Players then take turns beginning with Alex. On each turn, a player must play one card from their hand. The played card will either:

\begin{itemize}
    \item Be added to the pool of face-up cards, or
    \item Capture one or more cards from the pool, following these rules:
    \begin{itemize}
        \item A numeric card can capture a combination of numeric cards from the pool if their total sum equals 11.
        \item A Queen can only capture another single Queen. The same rule applies to Kings.
        \item A Jack captures all cards in the pool (including other Jacks), except for Kings and Queens.
    \end{itemize}
\end{itemize}

If a capture is possible, the player \emph{must} capture; they cannot simply add a card to the pool. Captured cards are retained and used to calculate each player’s score at the end of the game. Table~\ref{tab:score} outlines the scoring system used in Pasur. Notably, a \textbf{Sur}—defined below—grants a 5-point bonus.

A \textbf{Sur} occurs when a player captures all the cards from the pool in a single move. There are two important exceptions:
\begin{itemize}
    \item A Sur cannot be made using a Jack.
    \item Surs are not permitted during the final round of play.
\end{itemize}

\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Rule} & \textbf{Points} \\
\hline
Most Clubs & 7 \\
Each Jack & 1 \\
Each Ace & 1 \\
Each \;Sur & 5 \\
10{\color{red}\ding{117}} & 3 \\
2{\ding{168}} & 2 \\
\hline
\end{tabular}
\caption{Pasur Scoring System}
\label{tab:score}
\end{table}

\input{figs/game}
